Quantum Interval-Valued Probability: Measurement and Probability

### 2017-08-29 prop_iop.tex
prop_iop.tex \subsection{Between Expectation Values for Quantum Real-valued and Interval-valued Probability Measures} Updating...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[3] }
\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}

@@

Before discussing quantum IVPMs, we first review various notations
brought forward from conventional quantum theory. Assume that a physical
system is represented by a density matrix~$\rho$, and that we wish
to measure a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectral decomposition is given by
$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, where $P_{i}$ is the
projector onto the eigenspace of the eigenvalue~$\lambda_{i}$. Then,
the Born rule of CQT tells us that the expectation value of the observable~$\mathbf{O}$
is given by~\cite{544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
\end{equation}

@@

\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
if $\bar{\mu}$ is convex, then
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
\end{equation}
Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
holds for every observable, then $\bar{\mu}$ is convex.\end{thm}

\begin{proof}Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
it is easy to prove
\begin{eqnarray*}
\expval{\mathbf{O}}_{\bar{\mu}} & \stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=} & \int X\rmd\bar{\mu}'\\
 & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
 & \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.
\end{eqnarray*}
Therefore, equation~(\ref{eq:quantum-interval-expectation-core})
is equivalent to convexity if $\mathrm{core}\left(\bar{\mu}'\right)$
and $\coreBorn\left(\bar{\mu},\events'\right)$ are one-to-one correspondence
so that
\begin{equation}
\left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.
\end{equation}

@@

\begin{proof}Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
we have
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=}\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu'\right\} \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=}\left\{ \expval{\mathbf{O}}_{\mu}\right\} \,,
\end{equation}
where $\mu'=\mul[\prime]=\mur[\prime]$.\end{proof}

@@

\begin{proof}[Proof 2]Since $\left\{ \mathbf{O}_{j}\right\} $ is
a sequence of commuting observables, they can be diagonalized by a
common orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$,
i.e., $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$ and
$\prod_{j}\mathbf{O}_{j}=\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}$.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one $\proj{k}$
such that $\mu\left(\proj{k}\right)=1$.
\begin{equation}\eqalign{ 
 & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} =\prod_{j}\left\{ \lambda_{j,k}\right\} \\
= & \left\{ \prod_{j}\lambda_{j,k}\right\} =\expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,. 
}\end{equation}
\end{proof}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[3] }
\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}

@@

Before discussing quantum IVPMs, we first review various notations
brought forward from conventional quantum theory. Assume that a physical
system is represented by a density matrix~$\rho$, and that we wish
to measure a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectral decomposition is given by
$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, where $P_{i}$ is the
projector onto the eigenspace of the eigenvalue~$\lambda_{i}$. Then,
the Born rule of CQT tells us that the expectation value of the observable~$\mathbf{O}$
is given by~\cite{544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
\end{equation}

@@

\begin{thm}\label{thm:quantum-Rosenmuller}Given a Hilbert space
of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
if $\bar{\mu}$ is convex, then
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,.\label{eq:quantum-interval-expectation-core}
\end{equation}
Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
holds for every observable, then $\bar{\mu}$ is convex.\end{thm}

\begin{proof}Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
it is easy to prove
\begin{eqnarray*}
\expval{\mathbf{O}}_{\bar{\mu}} & \stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=} & \int X\rmd\bar{\mu}'\\
 & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
 & \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,.
\end{eqnarray*}
Therefore, equation~(\ref{eq:quantum-interval-expectation-core})
is equivalent to convexity if $\mathrm{core}\left(\bar{\mu}'\right)$
and $\coreBorn\left(\bar{\mu},\events'\right)$ are one-to-one correspondence
so that
\begin{equation}
\left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,.
\end{equation}

@@

\begin{proof}[Proof 1]Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
we have
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=}\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu'\right\} \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=}\left\{ \expval{\mathbf{O}}_{\mu}\right\} \,,
\end{equation}
where $\mu'=\mul[\prime]=\mur[\prime]$.\end{proof}

\begin{proof}[Proof 2]Let $\events'$ be the subspace of events
induced by $\mathbf{O}$. For any state\nb$\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
for all $P\in\events'$. Thus, $\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\expval{\mathbf{O}}_{\mu}$.
By theorem~\ref{thm:quantum-Rosenmuller}, we have
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]=\left\{ \expval{\mathbf{O}}_{\mu}\right\} 
\end{equation}
\end{proof}

@@

\begin{proof}[Proof 2]Since $\left\{ \mathbf{O}_{j}\right\} $ is
a sequence of commuting observables, they can be diagonalized by a
common orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$,
i.e., $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$ and
$\prod_{j}\mathbf{O}_{j}=\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}$.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one $\proj{k_{0}}$
such that $\mu\left(\proj{k_{0}}\right)=1$.
\begin{equation}\eqalign{ 
 & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\prod_{j}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} =\prod_{j}\left\{ \lambda_{j,k_{0}}\right\} \\
= & \left\{ \prod_{j}\lambda_{j,k_{0}}\right\} =\expval{\prod_{j}\mathbf{O}_{j}}_{\mu}\stackrel{\textrm{Lemma }\ref{lemma:expectation-singleton}}{=}\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,. 
}\end{equation}
\end{proof}
